University of Florida Knowledge Base Acceleration Notebook

### 2013-10-22 paper/kbanotebook2013/content/results.tex

 Our results are as follows: Document extraction using query entity matching with aliases, sentence 
extraction using alias matching and co-reference. Slot extraction using 
patterns, NER tags and NP tags. 158,052 documents with query entities, 17885 
unique extracted slot values for 8 slots and 139 entities, 4 slots and 31 
entities missing.

On the performance of the first submission run we performed random 
sampling via two processes, the results of which are according to
Table~\ref{table:initialresult}. You can view that we have had an accuracy of
around 55\%, and about 15\% wrong entity identified and 30\% incorrect value
extracted across all entities and slot types. For our final submission, we
provide a more detailed statistics, which has been elaborated in
Table~\ref{table:finalresultrecall} and Table~\ref{table:finalresultaccuracy}.
Table~\ref{table:finalresultrecall} shows the extent of search outreach for
each slot name. You can see that \textit{Affiliate} has been the slot name with
highest hits and \textit{CauseOfDeath} our lowest hit with 0 instances found
matching our patterns, after that \textit{AwardsWon} has been the next with 38
instances found. Table~\ref{table:finalresultaccuracy} addresses the relative
accuracy measure per slot value. There you can view that we have had the
highest accuracy of 63.6\% for \textit{AssociateOf} and the lowest of
1\% - 5\%  for \textit{Affiliate}, \textit{Contact\_Meet\_PlaceTime} and \textit{EmployeeOf}.

@@

\begin{table}
\caption{SSF Performance Measure on Initial Submission }
\centering
\label{table:initialresult}

@@

\begin{table}
\caption{Recall Measure on Submission Infer }
\centering
\label{table:finalresultrecall}
\begin{tabular}{|c|p{3.5cm}|p{4cm}|}
\hline 
 \textbf{Slot Name} & \textbf{Total instances of slot value found} & \textbf{\# of entities covered by slot value} \\ 
\hline 
Affiliate & 108598 & 80 \\ \hline 
AssociateOf & 25278 & 106 \\ \hline 
AwardsWon & 38 & 14 \\ \hline 
CauseOfDeath & 0 & 0 \\ \hline 
Contact\_Meet\_Entity & 191 & 8 \\ \hline 
Contact\_Meet\_PlaceTime & 5974 & 109 \\ \hline 
DateOfDeath & 87 & 14 \\ \hline 
EmployeeOf & 75 & 16 \\ \hline 
FoundedBy & 326 & 30 \\ \hline 
FounderOf & 302 &  29 \\ \hline 
Titles & 26823 & 118 \\ \hline 
TopMembers & 314 & 26 \\ \hline

@@

\begin{table}
\caption{SSF Accuracy Measure on Submission Infer }
\centering
\label{table:finalresultaccuracy}
\begin{tabular}{|c|c|c|c|}
\hline 
 \textbf{Slot Name}  & \textbf{Correct} & \textbf{Incorrect Entity name} & \textbf{Incorrect Value} \\ 
\hline 
Affiliate & 1\% & 95\% & 5\% \\ \hline 
AssociateOf & 63.6\% & 9.1\% & 27.3\%  \\ \hline 
AwardsWon & 10\% & 10\% & 80\%  \\ \hline 
CauseOfDeath & 0\% & 0\% & 0\%  \\ \hline 
Contact\_Meet\_Entity & 21\% & 42\% & 37\%  \\ \hline 
Contact\_Meet\_PlaceTime & 5\% & 20\% & 85\%  \\ \hline 
DateOfDeath & 29.6\% & 71\% & 25\%  \\ \hline 
EmployeeOf & 5\% & 30\% & 65\%  \\ \hline 
FoundedBy & 62\% & 17\% & 21\%  \\ \hline 
FounderOf & 50\% & 0\% & 50\%  \\ \hline 
Titles & 55\% & 0\% & 45\%  \\ \hline 
TopMembers & 33\% & 17\% & 50\%  \\ \hline

>>>>

We have 135 extraction patterns coverin each slot-name/entity-type combinations. Our final submission was named \textit{submission\_infer}. Our results are as follows: Document extraction using query entity matching with aliases, sentence 
extraction using alias matching and co-reference. Slot extraction using 
patterns, NER tags and NP tags. 158,052 documents with query entities, 17885 
unique extracted slot values for 8 slots and 139 entities, 4 slots and 31 
entities missing.

On the performance of our initial submission run we performed random 
sampling via two processes, the results of which are according to
Table~\ref{table:initialresult}. You can view that we have had an accuracy of
around 55\%, and about 15\% wrong entity identified and 30\% incorrect value
extracted across all entities and slot types. Most of our issues for this submission were regarding poor slot value extraction patterns and incomplete aliases whih were tried to be mtigated later on. For our final submission, we
provide a more detailed statistics, which has been elaborated in
Table~\ref{table:finalresultrecall} and Table~\ref{table:finalresultaccuracy}.
Table~\ref{table:finalresultrecall} shows the extent of search outreach for
each slot name. You can see that \textit{Affiliate} has been the slot name with
highest hits and \textit{CauseOfDeath} our lowest hit with 0 instances found
matching our patterns, after that \textit{AwardsWon} has been the next with 38
instances found. Affiliate is a very generic term and extracting real affiliates can be quite challenging using the extraction patterns provided. This can lead to noisy results. On the other hand for more precise terms our accuracy increases but we have less recall. Table~\ref{table:finalresultaccuracy} addresses the relative
accuracy measure per slot value. There you can view that we have had the
highest accuracy of 63.6\% for \textit{AssociateOf} and the lowest of
1\% - 5\%  for \textit{Affiliate}, \textit{Contact\_Meet\_PlaceTime} and \textit{EmployeeOf}.

@@

\begin{table}
\caption{SSF Performance Measure on \textit{initial\_submission} }
\centering
\label{table:initialresult}

@@

\begin{table}    
\caption{ Recall Measure on \textit{submission\_infer}: Generic slot names like affiliate had the most recall, compared to less popular slot names e.g. DateOfDeath }
\centering
\label{table:finalresultrecall}
\begin{tabular}{|c|p{3.5cm}|p{4cm}|}
\hline 
 \textbf{Slot Name} & \textbf{Total instances of slot value found} & \textbf{\# of entities covered by slot value} \\ 
\hline 
Affiliate & 108598 & 80 \\ \hline 
AssociateOf & 25278 & 106 \\ \hline 
AwardsWon & 38 & 14 \\ \hline 
CauseOfDeath & 0 & 0 \\ \hline 
Contact\_Meet\_Entity & 191 & 8 \\ \hline 
Contact\_Meet\_PlaceTime & 5974 & 109 \\ \hline 
DateOfDeath & 87 & 14 \\ \hline 
EmployeeOf & 75 & 16 \\ \hline 
FoundedBy & 326 & 30 \\ \hline 
FounderOf & 302 &  29 \\ \hline 
Titles & 26823 & 118 \\ \hline 
TopMembers & 314 & 26 \\ \hline

@@

\begin{table}
\caption{SSF Accuracy Measure on \textit{submission\_infer}: Accuracy of AffiliateOf was the best and Affiliate applied poorly due to ambiguity of being an affiliate of somebody/something }
\centering
\label{table:finalresultaccuracy}
\begin{tabular}{|c|c|c|c|}
\hline 
 \textbf{Slot Name}  & \textbf{Correct} & \textbf{Incorrect Entity name} & \textbf{Incorrect Value} \\ 
\hline 
Affiliate & 1\% & 95\% & 5\% \\ \hline 
AssociateOf & 63.6\% & 9.1\% & 27.3\%  \\ \hline 
AwardsWon & 10\% & 10\% & 80\%  \\ \hline 
CauseOfDeath & 0\% & 0\% & 0\%  \\ \hline 
Contact\_Meet\_Entity & 21\% & 42\% & 37\%  \\ \hline 
Contact\_Meet\_PlaceTime & 5\% & 20\% & 85\%  \\ \hline 
DateOfDeath & 29.6\% & 71\% & 25\%  \\ \hline 
EmployeeOf & 5\% & 30\% & 65\%  \\ \hline 
FoundedBy & 62\% & 17\% & 21\%  \\ \hline 
FounderOf & 50\% & 0\% & 50\%  \\ \hline 
Titles & 55\% & 0\% & 45\%  \\ \hline 
TopMembers & 33\% & 17\% & 50\%  \\ \hline
